### 2013-09-21 fig_mr_segs_vol.tex
3D slicer methods added

\begin{figure}[htb!]
\centering
\includegraphics[width=1.0\textwidth]{figs/MR_P79_SegsVol.eps}
\caption{Representative MR T2WI segmentations and rendered volume performed in
    3D Slicer, with the peripheral zone being delineated in red, and the
    central gland being delineated in blue.  The native imaging plane for
    segmentation is the axial view, shown in the bottom left image.  The bottom
    middle and right images show the projections of the rendered model segment
    outlines in the sagital and coronal views, respectively.}
\label{fig:mr_segs_vol} 
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\includegraphics[width=1.0\textwidth]{figs/MR_P79_SegsVol.eps}
\caption{Representative MR T2WI segmentations and rendered volume performed in
    3D Slicer, with the peripheral zone (PZ) being delineated in red, the
    central gland (CG) being delineated in blue, and the anterior fibromuscular
    stroma (AFS) being shown in gray.  The AFS was combined with the PZ for
    quantitative analyses shown herein.  The native imaging plane for
    segmentation is the axial view, shown in the bottom left image.  The bottom
    middle and right images show the projections of the rendered model segment
    outlines in the sagital and coronal views, respectively.}
\label{fig:mr_segs_vol} 
\end{figure}

### 2013-09-21 image_proc_methods.tex
3D slicer methods added

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
Axial T2W MR slices were manually segmented using the polygon tool on ITK SNAP
using separate labels for the peripheral zone (PZ), central gland (CG) and
anterior fibromuscular stroma (AFS). The gland was segmented from base to apex.
The base was identified below the bladder and subsequent images were segmented
until the last slice with visible prostatic tissue was identified caudally. The
CG, PZ and AFS were segmented independently according to their well-established
anatomical characteristics on
T2WI.~\cite{Verma2011,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location. Although not readily visible on every case, the AFS was identified by
its low T2 signal intensity and its location anterior to the central gland.

>>>>

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
Axial T2W MR slices were manually segmented using the polygon tool on
ITK-SNAP~\cite{Yushkevich2006} using separate labels for the peripheral zone
(PZ), central gland (CG) and anterior fibromuscular stroma (AFS). The gland was
segmented from base to apex.  The base was identified below the bladder and
subsequent images were segmented until the last slice with visible prostatic
tissue was identified caudally. The CG, PZ and AFS were segmented independently
according to their well-established anatomical characteristics on
T2WI.~\cite{Verma2011,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location. Although not readily visible on every case, the AFS was identified by
its low T2 signal intensity and its location anterior to the central gland.

ARFI images were segmented using a similar procedure to the MR images, using
XXXX (INSERT CRITERIA HERE).

Segmented image stacks were imported into 3D Slicer (v4.3.0, CITATION) and 3D
models were rendered using the following parameters (Table~\ref{tab:3dslicer}:

\begin{table}[htb!]
\centering
\caption{3D model volume rendering parameters}
\begin{tabular}{ll}
{\bf Parameter} & {\bf Value} \\ \hline
Decimation & 0.1 \\
Smoothing Algorithm & Laplacian \\
Smoothing  & 70.0 \\
Joint Smoothing & Enabled \\
\end{tabular}
\end{table}
